Methods to prioritise pop-up active transport infrastructure

### 2020-05-10 article.Rmd
Add results table

@@

```{r}

```

>>>>

The results of the method are summarised in Figure \@ref(fig:res) and Table 2.

@@

```{r}
res_table = r_pct_top_n %>% 
  sf::st_drop_geometry() %>% 
  select(name, length = group_length, cycling_potential, kkm_cycled) %>% 
  arrange(desc(kkm_cycled))
knitr::kable(res_table, caption = "The top 10 candidate roads for space reallocation for pop-up active transport infrastructure according to methods presented in this paper.", digits = 0)
```
